Towards a wide-coverage grammar for Swedish

### 2011-12-23 doc/report/report.tex
start on lexicon generation

The Swedish version of the Core Language Engine (CLE) \cite{gamback} % \cite{cle}
gives a full syntactic analysis as well as semantics represented in xx. A
translation to English  was implemented and the work was further developed in the spoken
language translator (xx,xx). Unfortunately, it is no longer available. The coverage of the Swedish
CLE is also reported to be very limited (Nivre,2002).\\

>>>>

The Swedish version of the Core Language Engine (CLE) \cite{gamback} % \cite{cle}
gives a full syntactic analysis as well as semantics represented in `quasi logical form'. A
translation to English  was implemented and the work was further developed in the spoken
language translator (xx,xx). Unfortunately, it is no longer available. The coverage of the Swedish
CLE is also reported to be very limited (Nivre,2002).\\
